\plaintitle

### 2016-05-18 paper/paper.tex
Start related work

The National Basketball Association (NBA) is the most famous and perhaps the best professional basketball league in the world. Like in every other sports branch, a lot of data and statistics about players, teams, games and seasons are available, mainly in large tables. Despite these tables contains a lot of information, it is very hard if not impossible, to interpret, compare efficiently and to gather insights in it. In our work we try to present this data in a whole different way. Therefore we have focused ourselves on some parts and not the entire available data.

@@

<Tell something more about the data in terms of tall/wide data
Mention that it's a time series
Tell something more about pre-processing steps (why?, did we change it over time?)
rfr to picture in 1st ppt sl 60>
\section{Related Work}\label{sec:literature}

Many visualizations of NBA data are focused on the "shot-chart".  This of individual players, multiple players together or all the teams
This is almost a standard in visualizations about NBA data where even the code for making short charts is easily found ~\cite{shotchartpython}~\cite{shotchartr}~\cite{shotchartapp}.

This paper (http://inf.ufrgs.br/~lsguedes/skooth/Publications_&_Works_files/nbavis_final.pdf) describes

@@

%General
%https://en.wikipedia.org/wiki/National_Basketball_Association
%http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado_MultipleViews_AVI00.pdf
%http://www.interactiondesign.us/courses/2011_AD690/PDFs/Shneiderman_1996.pdf
%http://workshop.sportvis.com/
%http://www2.parc.com/istl/groups/uir/publications/items/UIR-1986-02-Mackinlay-TOG-Automating.pdf
%http://www.cc.gatech.edu/~john.stasko/papers/infovis06.pdf

%Shot charts
%http://peterbeshai.com/buckets/app
%http://vorped.com/1-nba/2015-2016/player/6667/emmanuel-mudiay/
%https://github.com/amatlin/NBAvis
%https://thedatagame.com.au/2015/09/27/how-to-create-nba-shot-charts-in-r/
%http://savvastjortjoglou.com/nba-shot-sharts.html?utm_source=Python+Weekly+Newsletter&utm_campaign=5185ff0538-Python_Weekly_Issue_202_July_30_2015&utm_medium=email&utm_term=0_9e26887fc5-5185ff0538-312727397
%http://www.sloansportsconference.com/wp-content/uploads/2012/02/Goldsberry_Sloan_Submission.pdf
%http://vis.berkeley.edu/courses/cs294-10-sp10/wiki/images/archive/a/a2/20100511091342!Stephen_Chu_-_Information_Visualization_in_the_NBA_-_The_Shot_Chart_16.pdf
%http://toddwschneider.com/posts/ballr-interactive-nba-shot-charts-with-r-and-shiny/

@@

<Explain that this complies with the infovis seeking mantra: Overview, zoom&filter, details on demand
play-off view = overview
statistics view= details on demand
Talk about th organization of the 3 views + the choice for a tiled approach
- Each page is a 'tile' that we force with fixed scrolling
- Use of the keyboard is possible (space bar to scroll + arrows, arrows for timeline)
>

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
%\bibliographystyle{SIGCHI-Reference-Format}
\printbibliography

>>>>

The National Basketball Association (NBA) is the most famous and perhaps the best professional basketball league in the world. Like in every other sports branch, a lot of data and statistics about players, teams, games and seasons are available, mainly in large tables. Despite these tables contains a lot of information, it is very hard if not impossible, to interpret, compare efficiently and gather insights in it. In our work we try to present this data in a whole different way. Therefore we have focused ourselves on some parts and not the entire available data.

@@

<Tell something more about the data in terms of tall/wide data
Mention that it's a time series
Tell something more about pre-processing steps (why?, did we change it over time?)
rfr to picture in 1st ppt sl 60>

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/data}
  \caption{An overview of the data.}~\label{fig:data}
\end{figure}

\section{Related Work}\label{sec:literature}

On the IEEE Visualization Conference in 2013, the first workshop on sports data visualization was held \cite{ieeevis}. There is shown that the area of sport produces large amounts of data, which can be used for building visualizations and making analyses of the data. In the past visualizations of sports existed already, but there were not a lot of visualizations, and they were simple in the sense that they just represented the data without trying to give insights or to approach the data on a different way. There are some, but limited, sports-specific visualizations, like the basketball shot chart. This is a visualization frequentely seen when looking for visualizations about the NBA. Some shot chart vizualisations try to be different than others, but the general design and idea stays roughly the same. 
% 2 goeie papers die hierin verwerkt kunnen worden
%http://www.sloansportsconference.com/wp-content/uploads/2012/02/Goldsberry_Sloan_Submission.pdf
%http://vis.berkeley.edu/courses/cs294-10-sp10/wiki/images/archive/a/a2/20100511091342!Stephen_Chu_-_Information_Visualization_in_the_NBA_-_The_Shot_Chart_16.pdf

With our visualization we try to make it easier to interpret a collection of data about the NBA, and try to let users find patterns and insights in the data. A same kind of incentive was the start for \cite{cox2006sportsvis} who created a visualization to help people discover meaning in statistics generated during sporting events in the case of baseball.

@@

%Shot charts
%http://peterbeshai.com/buckets/app
%http://vorped.com/1-nba/2015-2016/player/6667/emmanuel-mudiay/
%https://github.com/amatlin/NBAvis
%https://thedatagame.com.au/2015/09/27/how-to-create-nba-shot-charts-in-r/
%http://savvastjortjoglou.com/nba-shot-sharts.html?utm_source=Python+Weekly+Newsletter&utm_campaign=5185ff0538-Python_Weekly_Issue_202_July_30_2015&utm_medium=email&utm_term=0_9e26887fc5-5185ff0538-312727397
%http://toddwschneider.com/posts/ballr-interactive-nba-shot-charts-with-r-and-shiny/

@@

<Explain that this complies with the infovis seeking mantra: Overview, zoom&filter, details on demand
play-off view = overview
statistics view= details on demand
Talk about th organization of the 3 views + the choice for a tiled approach
- Each page is a 'tile' that we force with fixed scrolling
- Use of the keyboard is possible (space bar to scroll + arrows, arrows for timeline)
- This papers are usefulle to refer to
http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado_MultipleViews_AVI00.pdf
http://www.interactiondesign.us/courses/2011_AD690/PDFs/Shneiderman_1996.pdf
http://www2.parc.com/istl/groups/uir/publications/items/UIR-1986-02-Mackinlay-TOG-Automating.pdf
>

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
%\bibliographystyle{SIGCHI-Reference-Format}
\printbibliography
%TODO References should be in alphabetical order and represented by numbers in the text.
